\speculake: Hiding Malware in Speculative Execution

### 2018-08-07 paper/figures.tex
update caption
added implementation section for spectre 1.1

\newcommand{\FigSpectreOne}{
\begin{figure}[t]
    \centering
    \includegraphics[width=0.9\linewidth]{figures/spectre_1_training.png}
    \caption{\textbf{Speculative buffer overflow warm-up}\,---\, %
    The direct branch predictor must
    be trained to expect that a branch will go a specific way before speculative
    buffer overflows can be used. We varied the number of times a branch was trained
    to be taken and observed the fraction of times we achieved a speculative buffer overflow
    execution immediately after (measured by observing if a speculatively-loaded value was present
    in cache avgeraged over 20,000 trials). We find that a branch must be trained in a
    direction at least 200 times before it can start to be used in a speculative buffer overflow.}
    \label{fig:spectre-one}
\end{figure}
}

>>>>

\newcommand{\FigSpectreOne}{
\begin{figure}[t]
    \centering
    \includegraphics[width=0.9\linewidth]{figures/spectre_1_training.png}
    \caption{\textbf{Speculative buffer overflow warm-up}\,---\, %
    The direct branch predictor must
    be trained to expect that a branch will go a specific way before speculative
    buffer overflows can be used. We varied the number of times a branch was trained
    to be taken and observed the fraction of times we achieved a speculative buffer overflow
    execution immediately after (measured by observing if a speculatively-loaded value was present
    in cache avgeraged over 20,000 trials). We find that a branch must be trained in a
    direction at least 400 times before it can start to be used in a speculative buffer overflow.}
    \label{fig:spectre-one}
\end{figure}
}

\newcommand{\FigSpectreOneModel}{
\begin{figure}[ht]
    \centering
    \includegraphics[width=0.9\linewidth]{figures/spectre_1_model.png}
    \caption{\textbf{Speculative Buffer Overflow}\,---\, %
    Safe input values are stored into a local array (Step 1),
    training the branch predictor to bypass the bounds check when given
    unsafe input (Step 2). This results in a speculative array store which
    overflows the bounds and overwrite a return address (Step 3). The CPU's 
    store-to-load forwarding will forward the speculative overflow to the 
    return (Step 4), where it will steer speculative execution to the 
    attacker-specified speculative entry point (Step 5). Eventually, the 
    original bounds check is resolved and control flow is redirected to the 
    cache timing function (Step 6). }
    \label{fig:spectre-one-model}
\end{figure}
}

### 2018-08-07 paper/implementation.tex
added implementation section for spectre 1.1

\subsection{Virtual Machine}
\label{subsec:spasm}

@@

>>>>

\subsection{Emulator}
\label{subsec:spasm}

@@

\subsection{Speculative Buffer Overflow Trigger}
\label{subsec:openssl-impl}

\FigSpectreOne

To demonstrate the adaptability of this attack we have implemented the 
Speculative Buffer Overflow alternative trigger and assembled an \speculake 
payload.

We make use of text input as the trigger to the payload program in this case,
where an input file contains entries specifying length, padding length,
and data value. When a line is read the payload program makes a bounds
check on the length of padding then stores the data at that offset in a
local array.

The local array store is now the vulnerability it can be exploited even 
with complete bounds checks. After a series of honest inputs we include 
an entry with a padding length beyond the maximum. On the runs with this
cafted input we flush from cache the maximum padding length constant in 
the payload program, preventing the bounds check from being resolved 
and allowing the data value to be speculatively stored. We 
then speculatively overwrite the return address and use store-to-load forwarding
to cause a following return to divert to the address specified by the data entry. 
From here we make use of the decryption gadget to dcecrypt SPASM instructions
from an encrypted data blob to be transmitted to the real world via cache 
side-channel. Using this method we have been able to run all SPASM payloads 
including the reverse-shell.

We note significant unpredictability in the branch predictor, though we
show in Figure~\ref{fig:spectre-one} that a minimum around 200 safe input entries
to each dishonest entry are required before a distinguishable signal is present 
in the cache channel.
